\documentclass[10pt, letterpaper]{article}

% Standard preamble using your formatting requirements
\usepackage[ignoreheadfoot, top=0.5 in, bottom=0.5 in, left=1 in, right=1 in, footskip=1.0 cm]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{fontawesome5}
\usepackage{ebgaramond}
\usepackage[colorlinks=true, urlcolor=primaryColor]{hyperref}

% Command for horizontal rule in section titles
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{0.4 cm}{0.3 cm}

\renewcommand\labelitemi{$\cdot$}

\newenvironment{highlights}{
    \begin{itemize}[topsep=0.10 cm, parsep=0.10 cm, partopsep=0pt, itemsep=0pt, leftmargin=10pt]
}{
    \end{itemize}
}

\begin{document}

% --- HEADER ---
\begin{center}
    \textbf{\fontsize{24 pt}{24 pt}\selectfont CINDY ZHANG} \\
    \vspace{0.3 cm}
    \normalsize
    \faMapMarker* Seattle, Washington \quad
    \href{mailto:cnmnzhang@gmail.com}{\faEnvelope[regular] cnmnzhang@gmail.com} \quad
    \faPhone* 320-266-0887 \quad
    \href{https://linkedin.com/in/cnmnzhang}{\faLinkedinIn cnmnzhang}
\end{center}

% --- EDUCATION ---
\section{EDUCATION}
\noindent \textbf{University of Washington} \hfill \textit{2025 – 2029 (expected)} \\
PhD in Biomedical Informatics and Medical Education (BIME) \\
\textit{Currently enrolled graduate student; meets all UW student staff requirements.}

\vspace{0.2 cm}

\noindent \textbf{Johns Hopkins University} \hfill \textit{2019 – 2023} \\
BS in Computer Science, BS in Biomedical Engineering with Honors

% --- RELEVANT EXPERIENCE (YOGA) ---
\section{RELEVANT EXPERIENCE}
\noindent \textbf{Instructor \& Teaching Assistant} \hfill \textit{June 2025 – Present} \\
\textit{\href{https://www.theyogashalaseattle.com/}{The Yoga Shala}}, Seattle, WA
\begin{highlights}
    \item Currently training and assisting in **Mysore Style Practice**, providing specialized, hands-on adjustments and one-on-one personalized instruction to individual practitioners in a group setting.
    \item Lead group classes focusing on physical asana and guided meditation, managing class flow for diverse skill levels.
    \item Collaborated on instruction at various external opportunities outside of the primary studio to expand community outreach and engagement.
    \item **Registered Yoga Teacher (RYT-200)**: Specialized in anatomy, alignment, and holistic mental/physical well-being.
\end{highlights}

% --- PROFESSIONAL EXPERIENCE ---
\section{PROFESSIONAL EXPERIENCE}
\noindent \textbf{Research Engineer} \hfill \textit{June 2024 – Present} \\
\textit{University of Washington Medical Center}, Seattle, WA
\begin{highlights}
    \item Develop and research adaptive AI models for blood markers, demonstrating deep understanding of human physiology and healthcare data.
    \item Ensure rigorous safety and data integrity standards within the UW medical ecosystem.
\end{highlights}

\vspace{0.2 cm}

\noindent \textbf{Team Lead} \hfill \textit{Jan 2021 – Nov 2021} \\
\textit{Delineo Disease Modeling}
\begin{highlights}
    \item Directed a simulation team of 5 people to optimize complex modeling workflows, improving output efficiency by 59\%.
    \item Managed project timelines, facilitated team communication, and provided leadership to reach community-focused goals.
\end{highlights}

% --- PUBLICATIONS ---
\section{PUBLICATIONS}
\noindent \textbf{Machine Learning and Artificial Intelligence-Based Clinical Decision Support for Modern Hematology}. \textit{Clinics in Laboratory Medicine} (In Press, 2025). Zhang C, Lam BD, Lucas F, Foy BH.

\vspace{0.1 cm}

\noindent \textbf{Haematologic Setpoints Are a Stable and Patient-Specific Deep Phenotype}. \textit{Nature}, Dec 2023. DOI: 10.1038/s41586-024-08264-5. PMID: 37808854. Foy BH, \textbf{Zhang C}, et al.

\vspace{0.1 cm}

\noindent \textbf{OPTIC: Optimizing Patient-Provider Triaging \& Improving Communications in Clinical Operations Using GPT-4 Data Labeling and Model Distillation}. \textit{arXiv}, Feb 2025. Santamaria-Pang A, \textbf{Zhang C}, et al.

\vspace{0.1 cm}

\noindent \textbf{Machine Learning Approach to Predict Emergent RV PV Loop Phenotypes in Pulmonary Hypertension}. \textit{Pulmonary Circulation}, accepted Feb 2025. Sivakumar N, \textbf{Zhang C}, et al.

\vspace{0.1 cm}

\noindent \textbf{Assessing Associations Between COVID-19 Symptomology and Adverse Outcomes After Piloting Crowdsourced Data Collection}. \textit{JMIR Formative Research}, Nov 2022. Flaks-Manov N, \textbf{Zhang C}, et al.

% --- PRESENTATIONS ---
\section{PRESENTATIONS}
\noindent \textbf{Modeling Physiologic Setpoints from Blood Tests to Quantify Human Regulation}. \textit{UW Scholars' Studio}, Seattle, WA, Nov 2025 (Speaker). Zhang C.

\vspace{0.1 cm}

\noindent \textbf{Adaptive AI Models for Personalized Laboratory Reference Intervals}. \textit{UW IMDS Symposium}, Seattle, WA, Feb 2025 (Speaker). Zhang C.

\end{document}